On The Difficulty of Computing Non-Commutative Signature Gröbner Bases

### 2021-12-26 article_issac.tex
Biblio.

\section{Introduction}

@@

@@

@@

>>>>

\section{Introduction}
Commutative part.
Modern algorithms:
\cite{F99,F5,FGLM}.
Survey \cite{EF17}
New take  \cite{G2V, GVW}
Applications \cite{LWXZ, CVV20, VVY21}

NC part.
Freaks \cite{MU00}.
Attempt \cite{K14}.
GVW for skew polynomial rings \cite{ZZ15}
Final complete
nc version \cite{HV21}.

@@

In this article,
we work with
the notations defined
in \cite{HV21}.

%Aller jusqu'à la Def 18
%de l'article HV

@@

  \bibitem{CVV20}
  Caruso, X., Vaccon T., Verron T.,
  \newblock {Signature-based algorithms for Gröbner bases over Tate algebras},
  \newblock {in Proceedings: ISSAC 2020, Kalamata, Greece.}

\bibitem{EF17}
Eder Christian and Faug{\`{e}}re Jean{-}Charles,
\newblock {A survey on signature-based algorithms for computing Gr{\"{o}}bner bases},
\newblock J. of Symbolic Computation, 2017

  \bibitem{F99}
  Faugère Jean-Charles,
  \newblock  {{A new efficient algorithm for computing Gröbner bases (F4)}},
  \newblock  {Journal of Pure and Applied Algebra}, {1999}

\bibitem{F5}
Faugère, Jean-Charles,
\newblock {A new efficient algorithm for computing Gröbner bases without reduction to zero (F5)},
\newblock{in Proceedings: {ISSAC'02}.}

  \bibitem{FGLM}
  Faugère, J.-C., Gianni, P., Lazard, D., Mora, T.,
  \newblock{Efficient computation of zero-dimensional Gr{\"o}bner bases by change of ordering},
  \newblock{J. of   Symbolic Computation 16~(4), 329--344, 1993}

  \bibitem{G2V}
Gao Shuhong, Guan Yinhua and Volny IV Frank,
\newblock{ A new incremental algorithm for computing Groebner bases},
\newblock{In Proceedings: {ISSAC'10}.}
%\newblock{ In Proceedings of the 2010 International Symposium on Symbolic and Algebraic Computation (ISSAC ’10). ACM, New York, NY, USA, 13–19.}

  \bibitem{GVW}
Gao Shuhong, Volny IV Frank, and Wang Mingsheng,
\newblock{ A new framework for computing Gröbner bases},
\newblock{ Mathematics of computation, 2016, vol. 85, no 297, p. 449-465.}

\bibitem{K14}
S.A. King,
\newblock {A non-commutative F5 algorithm with an application to the computation of Loewy layers},
\newblock {J. of Symbolic Computation} 65 (2014), pp. 111-129

  \bibitem{LWXZ}
  Lu Dong, Wang Dingkang, Xiao Fanghiu, Zhou Jie,
  \newblock  {{Extending the GVW Algorithm to Local Ring}},
  \newblock {Proceedings of 43th International Symposium on Symbolic and Algebraic Computation, {ISSAC}'18, New York, USA}

\bibitem{MU00}
E.Green, T. Mora, V.Ufnarovski,
\newblock The Non-Commutative Gröbner Freaks.
\newblock Symbolic Rewriting Techniques. Vol. 15.

\bibitem{HV21}
C. Hofstadler, T. Verron,
\newblock {
Signature Gröbner bases, bases of syzygies and cofactor reconstruction in the free algebra}, 
\newblock  	arXiv:2107.14675, 2021

@@

\bibitem{VVY21}
T.Vaccon, T.Verron, K.Yokoyama,
\newblock
{On affine tropical F5 algorithms},
\newblock {
Journal of Symbolic Computation},
Volume 102,
2021.

\bibitem{ZZ15}
X. Zhao, Y. Zhang,
\newblock {A signature-based algorithm for computing Gröbner-Shirshov bases in skew solvable polynomial rings}
\newblock Open Mathematics, Volume: 13, Issue: 1, 2015.
